---
title: "Bayes course repository"
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
library(emo)
```



Last update/recompile: `r Sys.time()`

Starting website/repository for a future course on bayesian analysis.

Right now mostly empty/placeholder pages and some links to resources.


# Acknowledgements

This course/site was developed and is maintained by [Andreas Handel](https://www.andreashandel.com/).

```{r, results = "asis", echo = FALSE, message = FALSE, warning=FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("bayesCoursecontributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{GithubID}](https://github.com/{GithubID})"),
    desc = ifelse(is.na(LastName), link, glue::glue("{FirstName} {LastName} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```



# License

The materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.](https://creativecommons.org/licenses/by-nc-sa/4.0/) Linked and embedded materials are governed by their own licenses. We assume that all external materials used or embedded here are covered under the educational fair use policy. If this is not the case and any material displayed here violates copyright, please let me know and we will remove it. 


